---
title: "R Notebook"
output: html_notebook
---

### Messing with Data types


I'm trying to learn how notebooks and markdown are treated differently in RStudio (if at all).

* https://blog.rstudio.com/2016/10/05/r-notebooks/

### Data Frames

```{r}
patientID <- c(1, 2, 3, 4)
age <- c(24, 45, 65, 40)
diabetes <- c("Type1", "Type2","Type1", "Type2")
status <- c("Poor", "Improved", "Excellent", "Poor")
patientdata <- data.frame(patientID, age, diabetes, status)
```

### Matrices

```{r}

m1 <- matrix(1:25)
m3d <- matrix(1:24, c(2,4,3)) #this doesn't work. Matrices are 2d
```

### Arrays


```{r}
a1 <- array(1:25)
a3d <- array(1:24, c(2,4,3))
```


### How to use Notebooks / Mardown

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

